R Packages to Aid in Handling Web Access Logs

### 2016-01-02 paper/paper.Rmd
Update paper.Rmd
Added missing space
Update paper.Rmd
typo

To solve this common problem in analysing request logs, the\CRANpkg{urltools} \citep{urltools} package was created. This contains a function,
\code{url\_decode}, which decodes URLs and relies on vectorised, compiled code to do so. Benchmarking the two approaches against each other shows that the \pkg{urltools} implementation is approximately 60-70 times faster over large datasets. Again using \pkg{microbenchmark}, if we compare the vectorised decoding of 1,000,000 URLs with \pkg{urltools} against \code{URLdecode} in a \code{vapply} loop, we see a 60-70 times speed improvement:

@@

The limitation of the package is that it some operations do not yet support IPv6 (since they require the storage of numbers bigger than R can currently handle).

>>>>

To solve this common problem in analysing request logs, the \CRANpkg{urltools} \citep{urltools} package was created. This contains a function,
\code{url\_decode}, which decodes URLs and relies on vectorised, compiled code to do so. Benchmarking the two approaches against each other shows that the \pkg{urltools} implementation is approximately 60-70 times faster over large datasets. Again using \pkg{microbenchmark}, if we compare the vectorised decoding of 1,000,000 URLs with \pkg{urltools} against \code{URLdecode} in a \code{vapply} loop, we see a 60-70 times speed improvement:

@@

The limitation of the package is that some operations do not yet support IPv6 (since they require the storage of numbers bigger than R can currently handle).
